How and Why to run a Hack Week

### 2017-08-18 sections/results.tex
Consolidate the three into one figure. Caption.

\begin{figure*}[htbp]
\begin{center}
\includegraphics[\textwidth]{fig/eval_techskills.png}
\caption{Self-reported technical learning outcomes at all three hack weeks}
\label{fig:techskills}
\end{center}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[\textwidth]{fig/eval_collab.png}
\caption{Hack week outcomes with respect to collaboration and peer-learning}
\label{fig:techskills}
\end{center}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[\textwidth]{fig/eval_openscience.png}
\caption{Changing attitudes towards open science at hack weeks}
\label{fig:techskills}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\begin{center}
\includegraphics[\textwidth]{fig/eval_techskills.png}
\includegraphics[\textwidth]{fig/eval_collab.png}
\includegraphics[\textwidth]{fig/eval_openscience.png}
\caption{{\bf Post-workshop surveys from three hack weeks}: participants in the 2016 astro-, geo- and neuro- hack weeks responded to questions assessing their experiences. We report here about results in three different domains: the development of technical skills (top), collaboration and learning (middle), and shifts in attitudes towards reproducibility and open science (bottom)}
\label{fig:survey}
\end{center}
\end{figure*}
